Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Include architecture diagram.
Turns out missing data is due to Heartbleed.
https://lists.torproject.org/pipermail/tor-dev/2014-May/006863.html

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-meek}
\caption{Number of concurrent users using the meek transport,
as reported by the Tor Metrics Portal.
Missing parts of the graph are caused by missing data at the metrics portal.
}
\label{fig:clients}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\linewidth]{architecture}
\caption{
System architecture.
The Google frontend server is the server that dispatches requests to different services depending on the Host header.
Components that are new in our system are outlined in blue.
The ``Google infrastructure'' block may be replaced by other infrastructure that supports domain fronting.
}
\label{fig:architecture}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-meek}
\caption{Number of concurrent users using the meek transport,
as reported by the Tor Metrics Portal.
The gap between April~14 and April~22 is when the Tor bridge authority
was down because of the Heartbleed OpenSSL vulnerability~\cite{heartbleed}, and wasn't collecting statistics.}
\label{fig:clients}
\end{figure}
